---
title: "Brief introduction to mcMST"
author: "Jakob Bossek"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Brief introduction to mcMST}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
```

# Quickstart

The **mcMST** package for the statistical programming language [R](https://www.r-project.org) contains methods for benchmark instance generation of multi-objective graph problems and methods for solving the multi-criteria spanning tree problem (mcMST).

## Generating a benchmark instance

Here we first generate a bi-criteria graph problem with n = 25 nodes. The first objective is the euclidean distance of node coordinates in [0, 10] x [0, 10] in the euclidean plane. The second objective follows a normal distribution with mean 5 and standard deviation 1.5. The instance generation process is modular and thus highly flexible (see the vignette on graph generation for details).
```{r, fig.width=6, out.width='100%', fig.cap='Plot of our bi-objective sample graph.'}
library(mcMST)
library(gridExtra)
set.seed(1) # reproducability
g = mcGP(lower = 0, upper = 10)
g = addCoordinates(g, n = 25, generator = coordUniform)
g = addWeights(g, method = "euclidean")
g = addWeights(g, method = "random", weight.fun = rnorm, mean = 5, sd = 1.5)
print(g)
plots = plotGraph(g)
plots$nrow = 1
do.call(grid.arrange, plots)
```

## Running an algorithm

Next, we apply a (10 + 10) genetic algorithm based on the Pruefer-number encoding as proposed by Zhou & Gen to approximate the Pareto-front for `max.iter = 100` generations.
```{r}
g = mcGP(lower = 0, upper = 10)
g = addCoordinates(g, n = 25, generator = coordUniform)
g = addWeights(g, method = "euclidean")
g = addWeights(g, method = "random", weight.fun = rnorm, mean = 5, sd = 1.5)
res = mcMSTEmoaZhou(g, mu = 10L, lambda = 10L, max.iter = 100L)
print(res$pareto.front)
ecr::plotFront(res$pareto.front)
```
